Add column names below bottom annotations in the heatmap
============================================

In the heamtap generated by [**ComplexHeatmap**](https://github.com/jokergoo/ComplexHeatmap) package, 
column names are drawn just below the heatmap body. If column annotations are put
at the bottom of the heatmap as well, the annotations will be put below the column names.
See following example:

```{r}
library(ComplexHeatmap)
set.seed(123)
mat = matrix(rnorm(100), 10)
foo = sample(letters[1:2], 10, replace = TRUE)
colnames(mat) = sapply(letters[1:10], function(x) paste(rep(x, 10), collapse = ""))
ha = HeatmapAnnotation(foo = foo)
Heatmap(mat, bottom_annotation = ha)
```

In order to put the column names below bottom annotations, you can do as follows:

1. suppress column names
2. add a text annotation which contains column names and put it as the last bottom annotation.

To correctly calcualte the height of column names, you need to use `max_text_width()` function.

```{r}
cn = colnames(mat)
ha2 = HeatmapAnnotation(foo = foo,
    cn = anno_text(cn, rot = 90, offset = unit(1, "npc") - unit(2, "mm"), just = "right"),
    annotation_height = unit.c(unit(5, "mm"), max_text_width(cn)))
Heatmap(mat, show_column_names = FALSE, bottom_annotation = ha2)
```

<!-- uid=Add_Column_names_below_Bottom_Annotations -->
