Adjust order or adding links to the Chord diagram
===================================================

```{r, echo = FALSE}
suppressWarnings(suppressPackageStartupMessages(library(circlize)))
```

Assuming following matrix:

```{r}
set.seed(123)
mat = matrix(sample(16, 16), 4, byrow = TRUE)
rownames(mat) = paste0("R", 1:4)
colnames(mat) = paste0("C", 1:4)
mat
```

The order of adding links is:

```
R1 -> C1
R2 -> C1
R3 -> C1
R4 -> C1
R1 -> C2
...
R4 -> C4
```

Actually if the input is a matrix, the matrix will be converted to a data frame:

```{r}
reshape2::melt(mat)
```

and add links for the first record to the last.

There are several scenarios that we need to adjust the default order:

1. we want to put the widest link on the most top,
2. we want to put the non-transparent links on the top.

These two scenarios are all for emphasizing certain links. If we have the data frame which
contains the interactions, we can adjust the order of rows to adjust the order of adding links
to the Chord diagram.

If it is a matrix, we can use `melt()` from **reshape2** package to convert it to a data frame:

```{r}
df = reshape2::melt(mat)
```

To make it simple, we define colors for sectors:

```{r}
grid.col = c("#00000040", "red", "#00FF0040", "#0000FF40", "orange", "pink", "yellow", "grey")
names(grid.col) = c(rownames(mat), colnames(mat))
grid.col
```

Following is the default Chord diagram. As you can see links from "R2" are complete red, it is
covered by links from "R3" and "R4" because "R3" and "R4" links are drawn later than "R2" links.

```{r}
library(circlize)
chordDiagram(df, grid.col = grid.col)
```

Next we adjust the order of rows of `df` to put "R2" links to the end, and then make the plot:

```{r}
df2 = df[c(which(df[[1]] == "R1"), which(df[[1]] == "R3"), which(df[[1]] == "R4"), which(df[[1]] == "R2")), ]
chordDiagram(df2, grid.col = grid.col)
```

Now the "R2" links are on the top, but the order of sectors changed that "R2" becomes the last sector in all "R*" sectors.
This problem can be simply solved by explictly setting `order` options:

```{r}
chordDiagram(df2, grid.col = grid.col, order = c(paste0("R", 1:4), paste0("C", 1:4)))
```

In a same way, if you want to put the widest link on the very top, just reorder the rows of the data frame by 
the associated absolute values.

```{r}
df3 = df[order(abs(df[[3]])), ]
chordDiagram(df3, grid.col = grid.col, order = c(paste0("R", 1:4), paste0("C", 1:4)))
```

However, there is one serious problem that the order of rows also affect the positioning of links on a sector. As you 
can see in above plot, the order of links on a sector is not very optimized that links are twisted. We want 
the left second red link to be moved to the most right on sector "R2".

From version 0.3.9, if the input is a data frame, the `chordDiagram()` recognize a `rank` column which defines the 
order of adding links (so here rank == 1 means draw first)

```{r}
df$rank = rank(abs(df[[3]]))
chordDiagram(df, grid.col = grid.col)
```

Or to put non-transparent links on the top:

```{r}
df$rank = ifelse(df[[1]] == "R2", 2, 1)
chordDiagram(df, grid.col = grid.col)
```

## Session info

```{r}
sessionInfo()
```

