Merge heatmap and annotation legends into a same column
=======================================================

In **ComplexHeatmap** package, legends for heatmap and annotations are differently treated
and they will be put in different places. However, if there are not too many heatmaps and annotations,
separating these two types of legends will be kind of waste of spaces.

In `draw()` method of `HeatmapList` class, there is an option `heatmap_legend_list` (or `annotation_legend_list`) which accepts
additional self-defined legends (in a form of `grob` objects). Thus, one strategy to merge
heatmap legends and annotation legends is to extract the legends first and suppress plotting legends, 
later we construct a list of legends and send to `heatmap_legend_list` argument.

In following example, there is only one heatmap and two simple column annotations.
When constructing column annotaiton `ha`, `show_legend` is set to `FALSE` to suppress annotation legends.

```{r, echo = FALSE, message = FALSE}
suppressWarnings(suppressPackageStartupMessages(library(ComplexHeatmap)))
```

```{r}
library(ComplexHeatmap)
library(circlize)
df = data.frame(type = c(rep("a", 5), rep("b", 5)),
                age = sample(1:20, 10))

ha = HeatmapAnnotation(df = df,
    col = list(type = c("a" = "red", "b" = "blue"),
               age = colorRamp2(c(0, 20), c("white", "red"))),
    show_legend = FALSE
)
```

Color mapping information is stored in `ha` and we can extract legends from `ha` object.

```{r}
all_annotation_name = sapply(ha@anno_list, function(anno) anno@name)
# in case not all annotations are simple annotations
l = all_annotation_name %in% c("type", "age")
anno_legend_list = lapply(ha@anno_list[l], function(anno) color_mapping_legend(anno@color_mapping, plot = FALSE))
anno_legend_list
```

Similar, `show_heatmap_legend` is set to `FALSE` when creating `ht` and legend object is extracted afterwards.

```{r}
mat = matrix(rnorm(80, 2), 8, 10)
ht = Heatmap(mat, name = "ht", top_annotation = ha, show_heatmap_legend = FALSE)
heatmap_legend = color_mapping_legend(ht@matrix_color_mapping, plot = FALSE)
```

Finally, `draw()` is called explicitely and a list of both heatmap legend and annotation legends are sent to
`heatmap_legend_list` option.

```{r}
draw(ht, heatmap_legend_list = c(anno_legend_list, list(heatmap_legend)))
```

## Session Info

```{r}
sessionInfo()
```
