Support raster image in heatmaps
==================================

Saving heatmaps in PDF format is kind of best parctice to preserve the quality. However,
when there are too many rows (say, > 10000), the output PDF file size would be huge and it takes
time and memory to read the plot.

Rendering heatmaps as raster images will effectively reduce
the file size. In `Heatmap()` function, there are four options which control how to generate
the raster image: `use_raster`, `raster_device`, `raster_quality`, `raster_device_param`. 

```{r matrix}
set.seed(123)
mat = matrix(rnorm(10000*100), ncol = 100)
```

Following make the heatmap with and without raster images.

```{r code, eval = FALSE}
library(ComplexHeatmap)
pdf("heatmap.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE)
dev.off()

pdf("heatmap_raster_by_png.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE, use_raster = TRUE, raster_device = "png")
dev.off()

pdf("heatmap_raster_by_jpeg.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE, use_raster = TRUE, raster_device = "jpeg")
dev.off()

pdf("heatmap_raster_by_tiff.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE, use_raster = TRUE, raster_device = "tiff")
dev.off()

pdf("heatmap_raster_by_CairoPNG.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE, use_raster = TRUE, raster_device = "CairoPNG")
dev.off()

pdf("heatmap_raster_by_CairoJPEG.pdf", width = 8, height = 8)
Heatmap(mat, cluster_rows = FALSE, cluster_columns = FALSE, use_raster = TRUE, raster_device = "CairoJPEG")
dev.off()
```

```{r, message = FALSE, results = "hide", echo = FALSE}
chunks <- knitr:::knit_code$get()
writeLines(c(chunks[["matrix"]], chunks[["code"]]), "raster_image_in_heatmaps.R")
system("Rscript raster_image_in_heatmaps.R")
file.remove("raster_image_in_heatmaps.R")
```

And the difference between these PDF files:

```{r}
all_files = c("heatmap.pdf", "heatmap_raster_by_png.pdf", 
	          "heatmap_raster_by_jpeg.pdf", "heatmap_raster_by_tiff.pdf",
	          "heatmap_raster_by_CairoPNG.pdf", "heatmap_raster_by_CairoJPEG.pdf")
fs = file.size(all_files)
names(fs) = all_files
sapply(fs, function(x) paste(round(x/1024), "KB"))
```

The ratio to `heatmap.pdf`:

```{r}
fs[-1]/fs[1]
```

```{r, echo = FALSE, results = "none"}
invisible(file.remove(all_files))
```

## Session Info

```{r}
sessionInfo()
```
