Reverse x-axis in the circular layout
======================================

In *circlize* package, x-axis in always clockwise in each sector, no matter it
is on the top of the circle or at the bottom. However, you can manually convert
the original positions on x-axis to pretend you have a reversed xaxis. Take folling example:

```{r, echo = -2}
library(circlize)
circos.clear()
circos.par(gap.degree = c(10, 10), start.degree = -5)
circos.initialize(factors = c("a", "b"), xlim = c(0, 1))
circos.trackPlotRegion(ylim = c(0, 1), panel.fun = function(x, y) {
	circos.axis(major.at = seq(0, 1, by = 0.1))
})
circos.rect(0.2, 0.2, 0.4, 0.4, col = "red", sector.index = "a")
circos.link("a", 0.3, "b", 0.7)
circos.clear()
```

In the bottom sector, the order of x-axis seems not very convinient to read.
Actually we can make some transformation on the original coordinates on x-axis.
In following we defined `reverse_xaxis()` which flips the axis.

```{r}
reverse_xaxis = function(x, xlim) {
	(xlim[2] - xlim[1]) - (x - xlim[1]) + xlim[1]
}
reverse_xaxis(seq(0, 1, by = 0.1), xlim = c(0, 1))
```

Now we apply `reverse_xaxis()` to all the coordinates in the sectors we want to
flip.

```{r}
circos.par(gap.degree = c(10, 10), start.degree = -5)
circos.initialize(factors = c("a", "b"), xlim = c(0, 1))
circos.trackPlotRegion(ylim = c(0, 1), panel.fun = function(x, y) {
	sector.index = get.cell.meta.data("sector.index")
	xlim =  get.cell.meta.data("xlim")
	if(sector.index == "a") {
		circos.axis(major.at = seq(0, 1, by = 0.1), labels = reverse_xaxis(seq(0, 1, by = 0.1), xlim))
		circos.rect(reverse_xaxis(0.2, xlim), 0.2, reverse_xaxis(0.4, xlim), 0.4, 
			col = "red", sector.index = "a")
	} else {
		circos.axis(major.at = seq(0, 1, by = 0.1))
	}
})
xlim = get.cell.meta.data("xlim", sector.index = "a")
circos.link("a", reverse_xaxis(0.3, xlim), "b", 0.7)
circos.clear()
```

## Session info

```{r}
sessionInfo()
```

<!-- uid=reverse_xaxis -->
