Use closure to store variables locally
========================================

Assuming following scenario: we first construct a list of functions in a `for` loop that
each function does some job and also tracks the status of each iteration. Later all the functions
in the list will be executed sequentially. This scenario is not rare e.g. when making a complex
genomic plot with multiple tracks that each track accepts a self-defined graphic function. All
self-defined functions are firstly recorded and put into a wrapper object and in the end, a plotting
function is applied to execute all the graphic functions. Following code shows an example:

```{r, eval = FALSE}
for(i in 1:n_track) {
	new_track = add_new_track(..., fun = function() {
		...
		cat("this is track", i, "\n")
	})
	obj = add_obj(obj, new_track)
}
plot_tracks(obj)
```

However, `i` in the self-defined functions does not have the value you expect. Actually `i` always has
the value `n_track`. Let's do following simplified experiment:

```{r}
f_list = list()
for(i in 1:4) {
	f_list[[i]] = function() print(i)
}

for(k in 1:4) {
	f_list[[k]]()
}
```

Unfortunately, the function always gets the value of 4 which is the last number of the for loop. 

The reasion is when the function is defined, the variables inside the function will not be evaluated unless they
are executed, so in the `function() print(i)`, the value of `i` is not recorded when it is defined, and when it is called,
it looks for `i` in the current environment and the four iterations have been already finished and `i` has the value of 4.

In order to catch the value of `i` in each iteration, we can use closure to catch it and stored it locally. In following
example, a copy of `i` is stored in a local environment which is associated with the function defined in each iteration.
Later on, when the function is executed, it will look for the `i` in the environment where it is defined and it is
exactly the local environment it is associated.

```{r}
f_list = list()
for(i in 1:4) {
	f_list[[i]] = local({i = i; function() print(i)})
}

for(k in 1:4) {
	f_list[[k]]()
}
```
